DraftDataAnalysis

### 2023-04-14 DraftDataAnalysis.Rmd
Add files via upload

draft = draft %>%
  mutate(Pos = replace(Pos, Pos == "S", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "CB", "DB"))
```

@@

b = reg2$fitted.values
PickValue = tibble(wAV = b, Pick = 1:4489)
PickValue = PickValue %>%
  filter(Pick < 256)
PickValue
```
```{r}
draftPick %>%
  filter(Draft > 1993) %>%
  group_by(Rnd) %>%
  summarise(averagewAV = mean(wAV))
```

@@

```{r}
draft %>%
  filter(Player == "Tre'Davious White")
```

>>>>

#draft = draft %>%
  #mutate(Pos = replace(Pos, Pos == "S", "DB")) %>%
  #mutate(Pos = replace(Pos, Pos == "CB", "DB")) %>%
  #mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  #mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  #mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  #mutate(Pos = replace(Pos, Pos == "OLB", "LB")) %>%
  #mutate(Pos = replace(Pos, Pos == "ILB", "LB"))
```
```{r}
draft %>%
  filter(Pos == c("K")) %>%
  #filter(wAV <= 9) %>%
  filter(wAV >= 35) %>%
  summarise(averageAP1 = mean(AP1), averagePB = mean(PB), averageSt = mean(St), averageG = mean(G), averageCompPer = mean(Cmp/PassAtt), averagePassYds = mean(PassYds), averagePassTds = mean(PassTD), averageIntO = mean(`Int(O)`), averageRushYds = mean(RushYds), averageRushTds = mean(RushTD), averageRec = mean(Rec), averageRecYds = mean(RecYds), averageRecTds = mean(RecTD), averageSolo = mean(Solo), averageIntD = mean(`Int(D)`), averageSk = mean(Sk))
```

@@

b = reg2$fitted.values
PickValue = tibble(Pick = 1:4489, wAV = b)
PickValue = PickValue %>%
  filter(Pick < 256)
PickValue
```

```{r}
draftPick %>%
  filter(Draft > 1993) %>%
  group_by(Rnd) %>%
  summarise(averagewAV = mean(wAV))
```
```{r}
draftPick %>%
  group_by(Pick) %>%
  summarise(averagewAV = mean(wAV))
```

@@

```{r}
draft %>%
  filter(Pos == c("K"))%>%
  arrange(desc(wAV))
draft %>%
  filter(Player == "Cameron Heyward")
```

Which Positions have the most value?
```{r}
draft %>%
  group_by(Pos) %>%
  summarise(averagewAV = mean(wAV)) %>%
  arrange(desc(averagewAV))
```
Which was the best NFL draft?
```{r}
draft %>%
  group_by(Draft) %>%
  summarize(sumwAV = sum(wAV)) %>%
  arrange(desc(sumwAV))
draft %>%
  filter(Draft == 2009) %>%
  arrange(desc(wAV))
draft %>%
  filter(Pos == "WR") %>%
  filter(wAV == 4)
```
When do positions tend to get drafted?
```{r}
draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  group_by(Pos) %>%
  summarise(avgDraftPos = mean(Pick)) %>%
  arrange(avgDraftPos)
```
When the first player at each position gets picked on average?
```{r}
draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  arrange(Pick) %>%
  group_by(Pos, Draft) %>%
  mutate(NumPosInDraft = n()) %>%
  mutate(PosDraft = 1:NumPosInDraft) %>%
  arrange(PosDraft) %>%
  ungroup(Draft) %>%
  filter(PosDraft == 1) %>%
  summarise(avgPick = mean(Pick)) %>%
  arrange(avgPick)
```

When should positions really be drafted?
```{r}
draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Draft < 2011) %>%
  filter(Rnd == 1) %>%
  group_by(Pos) %>%
  summarize(avgwAV = mean(wAV)) %>%
  arrange(desc(avgwAV))
```

Position: T
```{r}
draftT = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "T") %>%
  filter(Draft < 2011) %>% 
  arrange(Pick)

attach(draftT) 
reg1 = lm(draftT$wAV~draftT$Pick)
reg2 = lm(draftT$wAV~log(draftT$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

draftT %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )

reg = lm(draftT$wAV~log(draftT$Pick))

b = predict(reg)
PickValue = tibble(Pick = 1:350, wAV = b)
PickValue = PickValue %>%
  filter(Pick < 256)
PickValue
```
```{r}
draftT = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "T") %>%
  filter(Draft < 2011)

attach(draftT) 
reg1 = lm(draftT$wAV~draftT$Pick)
reg2 = lm(draftT$wAV~log(draftT$Pick))
jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

draftT %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~log(x),
              se = TRUE,
              )

draftQB = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "QB") %>%
  filter(Draft < 2011)

draftDE = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == "DE") %>%
  filter(Draft < 2011)
```
```{r}
draftPos = draft %>%
  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
  filter(Pos == c("T", "QB", "DE")) %>%
  filter(Draft < 2011)

draftPos %>% ggplot(aes(x = Pick, y = wAV)) +
  geom_jitter(aes(draftT$Pick, draftT$wAV), colour = "red") + 
  stat_smooth(aes(draftT$Pick, draftT$wAV, col = "red"),
              method = lm,
              formula = y~log(x),
              se = TRUE,
              ) +
  geom_jitter(aes(draftQB$Pick, draftQB$wAV), colour = "blue") + 
  stat_smooth(aes(draftQB$Pick, draftQB$wAV, col = "blue"),
              method = lm,
              formula = y~log(x),
              se = TRUE,
              )
```
```{r}
draft %>%
  filter(Player == "Joe Webb")
```
